\documentclass[12pt]{article}
\usepackage{sd}

\title{Stadium Traffic}
\team{13}
\addauthor{Parth Doshi;parthd@seas.upenn.edu}
\addauthor{Zain Mukaty;zmukaty@seas.upenn.edu}
\addauthor{Felipe Ochoa;felipeo@seas.upenn.edu}
\advisor{Dr. Andrew E. Huemmler;huemmler@seas.upenn.edu}
\reportname{Phase 2 Project Report}
\addbibresource{sources.bib}

\begin{document}
\maketitle
\abstract

\input{includes/abstract.tex}

\newpage

\tableofcontents

\newpage

\mainmatter

\section{Introduction}

\input{includes/intro.tex}

\section{Discussion of Previous Work}

\input{includes/previous-work.tex}


\section{Strategic Plan/Structure}

\input{includes/strategic-plan.tex}

\addtocounter{subsection}{1} %\subsection{Test and Demonstration}
%\subsubsection{Test}
%\subsubsection{Demonstration}

\subsection{Schedule}
The schedule consists of the different tasks that we estimate we will
need to accomplish in order to have a successful project. The tasks
can be broken into

\begin{itemize}
  \item Planning and design
  \item Creating the required subsystems
  \item Integrating the subsystems into one system
  \item Implementation.
\end{itemize}

Each task is assigned to only one individual although others may also
be working on the tasks, but the assigned individual is accountable to
get it done correctly and on time. Based on the Gantt chart and
schedule it is clear that we aim to work consistently over the course
of the year to meet the milestones (course requirements) and also aim
to get some work done over winter break so that we don’t fall behind
schedule.

We are currently ahead of schedule in some tasks, and behind schedule
in other tasks. This is similar to our situation when we submitted the
first project report because we are facing similar obstacles in
obtaining required information to progress in certain areas. However,
this is not as much of a concern to us as being completely behind
schedule because we can alter resource allocation to reconcile the
variance and bring the project back on schedule.

The two areas where we are behind schedule are:

\begin{enumerate}[label=(\emph{\alph*})]
  \item Working with the Philles/Eagles
  \item Working with the Philadelphia Police Department.
\end{enumerate}

This can be attributed to the major constraint mentioned in the
introduction. Dr. Huemmler has been trying to get us in touch with
them, but so far they have not been very responsive.

On November 16th, 2012, Dr. Huemmler sent letters on SEAS letterhead
paper to the following five individuals in these organizations:
\begin{description}[style=nextline]
    \item[Mike DiMuzio]
  Director of Operations/Facilities, Philadelphia Phillies
    \item[Julie Hershey]
  Community Relations, Philadelphia Eagles
    \item[Zach Hill]
  Senior Director of Communications, Philadelphia Flyers
    \item[Michael Preston]
  Director of Public Relations, Philadlephia 76ers
    \item[Lt. John Hewitt]
  PSA Lieutenant
\end{description}

Dr. Huemmler assures us that we will have meetings set up for the
middle of January, when we return from winter break. We have formed a
contingency plan, and updated the schedule so that we can allocate
more time to this to bring us back on schedule once we have
established contact. We plan to devote more resources to the subtasks
that rely on the meetings in order to bring the project back on
schedule.

Although the delay in contract with the Eagles and Philadelphia PD
lead us to fall behind in certain areas, we were able to reallocate
the time and resources that should have been used there, to other
tasks. These tasks include the SEPTA subsystem and GHG emissions
subsystem. Although we had originally planned to start these later in
this semester and next semester (respectively), we were able to start
and make progress on both of these subsytems during this semester.

Another factor that helped us get ahead of schedule in these areas was
the fact that we over-estimated the time to complete specific
tasks. The specific tasks that we over-estimated were the research to
find the necessary data for the GHG emissions subsystem and the
programming aspect of the SEPTA subsystem.

Overall, at the end of the first semester we have made significant
progress, which is discussed in more detail in the Results section. We
have defined our problem and scope, designed our systems approach and
began building two of the subsystems. We also plan to have some work
done over winter break, and consolidate our efforts at the beginning
of next semester and revise our schedule accordingly.

\section{Preliminary Results}
As discussed in the schedule discussion in section 3.5, we have made
significant progress on our project that will be critical to
supporting our efforts in Phase 2. We have had four main outcomes from
Phase 1 that we hope to carry forward.

\subsection{Project scope and determination of target user}

Our project started off with the aim of reducing CO2 emissions from
cars idling in parking lots after sports games. Over the course of
Phase 1, we have broadened our scope to develop a system to reduce GHG
emissions as a byproduct of fans travelling to and from sports
games. This broad aim will be carried forward to Phase 2 to drive us
to find innovative solutions to problems that we face by keeping the
overall goal in mind.

Through the semester, we have also determined three possible target
users for the finished product from our project:

\begin{descenum}
    \item[Philadelphia Sports Teams] (Eagles/Phillies/Flyers) We could
develop an interface that would allow the management of these teams to
determine the impact of various incentives towards reducing GHG
emissions.

  \item[Philadelphia Police Department] We could develop a mock-up of
an application that would help streamline traffic direction for fans
leaving stadiums

  \item[Sports Fans] We could develop a web interface/mock-up that would
allow users to understand the GHG emission impact of their travels and
alternatives to reduce this impact.
\end{descenum}

Our work in Phase 2 will involve determining which target user would
be the best choice to focus on given the availability of data and
involvement of the sports teams (as talked about before in the
report).

\subsection{Overall systems approach}
As discussed in section 3.1, we
have developed an overall systems approach to the project that we will
be using to guide our progress next semester. The system block diagram
will be used to understand how each module fits into the overall
system and will help prioritize among competing choices for time
allocation.

\subsection{SEPTA Subsystem}
Through Phase 1, we have developed a comprehensive database of all
SEPTA rail, trolley and transit stations and the lines that operate
across these stations. This data is stored in a well-typed XML based
on a DOM that ensures that all required fields are present for each
station. This database will be used to support further development of
the train model in calculating the emissions from the train system as
well as travel time alternatives when suggesting substitution of car
travel with train travel.

\subsection{GHG Emissions Subsystem}
Through Phase 1, we
have developed a comprehensive plan to create the GHG emissions
subsystem. The discussion above already detailed the creation and
design of the system, including the input, transfer function and
output for each of the five iterations. This plan will be used in
Phase 2 to program the subsystem and create a working model of the GHG
emissions subsystem.

\addtocounter{section}{1} % \section{Lessons Learned}

\section{Equipment/Fabrication/Software Needs}
We do not have any need for specialized equipment or software. The
software we will be using is either publicly available, or available
at Penn. We expect that our production version of the model will not
depend on commercial tools.

\addtocounter{section}{1} % \section{Conclusions and Recommendations}

\section{Nomenclature}
{\centering
\midcolumnwidth=.8\textwidth plus 10\tabcolsep minus 10\tabcolsep
\begin{tabular}{%
    >{\raggedright\bfseries}p{.1\textwidth}%
    p{\midcolumnwidth}}
  API & Application programming interface. An official, documented way
  for a program to access a database or another program, such as that
  of Google Maps. \\
  DOM & Document Object Model. A file format that is very easy to
  parse and yet human-readable. \\
  EPP & Emissions per passenger. \\
  EPM & Emissions per mile. \\
  GHG & Greenhouse gases. We mostly mean Carbon Dioxide, but we use
  the term GHG since emissions are highly correlated across types in
  this application. \\
  HBO & Home-based other. A category of trips in the
  standard  model. Contrast with HBS, HBW, NHO, and NHW. \\
  HBS & Home-based shop. A category of trips in the standard
  model. Refers to trips from the home to go shopping. Contrast with
  HBO, HBW, NHO, and NHW. \\
  HBW & Home-based work. A category of trips in the standard
  model. Refers to trips from the home to go to work. Contrast with
  HBO, HBS, NHO, and NHW. \\
  MAG & Maricopa Association of Governments. It is in charge of
  transportation planning for Phoenix and it surroundings. \\
  NHO & Non-home-based other. A category of trips in the standard
  model. Contrast with  HBO, HBS, HBW, and NHW. \\
  NHW & Non-home-based work. A category of trips in the standard
  model. Refers to trips not from the home to go to work. Contrast
  with HBO, HBS, HBW, and NHO. \\
  SEPTA & Southeast Pennsylvania Transit Authority. Manages the
  commuter rail, the subway, trolley, and bus systems in and around
  Philadelphia \\
  SQL & A type of database that is commonly used. \\
  TAZ & Traffic analysis zone. Used in modeling the UTMS. It involves
  dividing a geographical area into units that have sufficiently
  similar transit and demographics to treat as one for the purposes of
  the model. \\
  UTMS & Urban Transportation Modeling System. A commonly used
  framework to model traffic demand and flows. \\
  XML & Extensible markup language. A structured file format that is
  human-readable and easily parseable and customizable. \\
\end{tabular}
}

\makereferences

\makebibliography


\section{Financial Information}
We expect our project to incur minimal cost. At this time, the only
foreseeable expenses are the cost of transportation to the
stadium. Depending on how we refine the user needs after our meeting
with the Eagles, we may have to purchase a mobile device on which to
prototype our model interface.

%\section{Ethical Issues}

\appendix

\section{A Documented Module of Code}
\lstinputlisting[language=python,basicstyle=\small]{includes/module.py}
\end{document}

%  LocalWords:  DOM EPP EPM GHG Huemmler Vukan Vuchic ITE
