
\subsection{Description of Larger Context}

There are a lot of important stakeholders involved with the
project. These include the sports fans who are the potential end users
and will input personal data into the system and receive outputs, the
sports teams (Philadelphia Phillies, Eagles and Flyers) who are
undertaking initiatives with similar goals and SEPTA who will have
more passengers if our project is a success.


\subsection{Analysis of Ethical Issues}

There are a number of ethical issues that may arise when our project
is launched to the public. The first obvious issue arises with the
conflict of interest with the parking lots. If more people take SEPTA
then it will reduce their revenue and they would not be happy with it
and may even have to charge higher prices to the people who continue
to drive. Item 2 in the IEEE Code of Ethics says ``to avoid real or
perceived conflicts of interest whenever possible, and to disclose
them to affected parties when they do exist;'' and even the INCOSE Code
of Ethics says ``Avoid conflicts of interest and the appearance
thereof.'' Since we are affecting their business, we are harming them,
which is in conflict with the ACM Code of Ethics section 1.2 Avoid
harm to others. Furthermore, it may even be a conflict of interest
with the sports teams and other food or merchandise vendors who make
money when people tailgate and promote the experience, because if
people don’t drive then they can’t tailgate. The above sections of all
three codes of ethics are also relevant to this.

Another concern may arise because of the links to other websites for
carpooling and buying carbon offsets. If there is any legal issues
that arise from the misconduct websites, we do not want to be held
liable so it is important to have a disclaimer that is clearly visible
and explicitly states that we are not affiliated with those websites
in anyway. One potential legal issue would be if it is found out that
the carbon offsets website is misusing the donations. This could
transfer over to us if we are known to be affiliated with them, so we
need to make sure we are not. A similar liability could arise from
the carpool website if there were any security lapses that arise. That
is why it is important to make sure that we have no legal connection
with them and make that clear on our website. This would also be in
line with the IEEE first code of conduct that states ``to accept
responsibility in making decisions consistent with the safety, health,
and welfare of the public, and to disclose promptly factors that might
endanger the public or the environment'' and the INCOSE code that
states ``Accept responsibility for your actions and engineering
results, including being open to ethical scrutiny and assessment.''

Misleading our users has some ethical ramifications that is why it
should be clear what information we are providing and how it was
calculated. Two areas that could be potentially misleading are
providing zero carbon emissions from SEPTA on the website, which we
have to make clear are the marginal emissions because the train will
be running anyways. It would be wrong to make the user believe that
SEPTA produces no emissions. The other area that could be misleading
is when we provide an approximate driving and SEPTA travel time,
because this is based on data from a simulation for an average car and
the time may vary greatly for any specific car depending on where
exactly they park. Therefore this must be made clear. These are in
line with the IEEE Code of Conduct sections 3 and 6 that state ``to be
honest and realistic in stating claims or estimates based on available
data'' and ``to maintain and improve our technical competence and to
undertake technological tasks for others only if qualified by training
or experience, or after full disclosure of pertinent limitations''
respectively. Even the following INCOSE Code of Ethics items are
relevant: ``Act legally, honorably, honestly, justly, and
responsibly'' and ``Give prudent advice. Be truthful, objective, and
maintain your professional and technical integrity.''

We should also make sure to attribute Google for the data that we get
from Google Maps API because the ACM Code of Ethics section 1.6 says
that we should ``Give proper credit for intellectual property.''

\subsection{Recommendations}

The most pressing concerns are those of the legal liability from third
party websites and the conflict of interest with the parking lot
owners. There are possible legal or market-based solutions. We could
have disclaimers showing no affiliation with the websites and do our
own due diligence on any websites that we provide links to. For the
conflict of interest, we could consult a lawyer to make sure that no
legal action can be taken against us by the parking lot operators if
their sales are affected. We could also work together with the parking
lot to provide them with other sources of income such as organization
of tailgating services for people who take SEPTA and don’t have
cars. We could also work with the sports teams to get compensation for
helping them reduce traffic and achieve their goals of becoming more
environmentally friendly and split some of that remuneration with the
parking lot operators. Finally, the last ethical concern arising from
misleading users can be easily mitigated by clearly stating our method
and assumptions used to calculate the output. This way the user would
be informed and not misunderstand anything.
