The schedule consisted of the different tasks that we estimated we
would need to accomplish in order to have a successful project. The
tasks can be broken into

\begin{itemize}
  \item Planning and design
  \item Creating the required subsystems
  \item Integrating the subsystems into one system
  \item Testing and validation
\end{itemize}

Each task was assigned to only one individual although others may also
have been working on the task, but the assigned individual was
accountable to get it done correctly and on time. Based on the Gantt
chart and schedule it is clear that we aimed to work consistently over
the course of the year, including winter break, to meet the milestones
(course requirements) and not fall behind schedule. Although there
were delays in completing some tasks, we did not let that disrupt our
uniform workflow by reallocating resources to other tasks and either
getting them started early or completed faster by having more people
working on it.

The main challenge that we faced was the delay and inability to
establish contact with the Philadelphia Phillies or Philadelphia
Police Department. The lack of contact had lead us to postpone some of
our earlier tasks till we met them to understand their requirements
and get the required data from them. Our advisor, Dr. Huemmler, worked
very hard to try to get us in contact with them and sent multiple
emails and even letters on official University of Pennsylvania SEAS
letterhead to five people at the Phillies and Police department, but
still did not manage to schedule a meeting.

Finally, during mid March, we reached our deadline to determine the
end users and had to disregard the Phillies and make the sports fans
the end users. This lead two major consequences for the schedule:

\begin{enumerate}
  \item Changing some of the originally scheduled tasks
  \item Non-uniform distribution of work
\end{enumerate}

Since the end users changed, there were certain aspects of the system
that needed to be removed and other subsystems and functionalities
that had to be added to accommodate the change in requirements. The
Incentive Scheme or Tailgate Model had to be removed because now we no
longer had to determine the effect of various incentive schemes on
trip distribution or modal distribution. However, we had to develop a
website for the front end that synthesized the information from the
simulation and GHG (Green House Gas) Emissions model. We also had to
increase the scope of the SEPTA model to incorporate the entire SEPTA
system rather than just the station level model for AT\&T
Station. Finally, we had to incorporate travel time into both the
SEPTA and Car models because that would be an important output for the
end user.

Due to this major change when there was approximately one month
remaining before demo day, there was a lot of work that needed to be
done and we had to allocate more time to the project that we had
originally scheduled. However, we were able to do this for two main
reasons. Firstly, we had anticipated this and as accordingly set a
contingency plan, which involved pushing some tasks back that were the
same for both systems, and pushing other tasks forward that were
specific to either one of the systems. Secondly, when we were
originally making the schedule we had kept slack time in the
tasks. There was a third unanticipated factor of over-estimating the
time it would take to complete certain tasks, which helped us at the
end. We had over-estimated the time it would take to make the SEPTA
subsystem and GHG Emissions model, however, the time we had saved in
making the model originally, we spent on updating it to suit the new
requirements. However, developing the new front-end system took a lot
of time and lead to greater than proportionate time spent on the
project in April.

Despite the late scheduling changes, we managed to have a working
model and front-end website by demo day. However, if we were to do
this again we would have set the deadline to determine the end user to
a much earlier date, such as the end of first semester. This would
have given us more time to refine the front-end and even launch the
website before demo day in order to get user feedback and incorporate
that into our model. However, we used alternative methods of testing
and validation.

