Test
The goal was to test every aspect of the system specifciation as stated in section 3.2.

The python \'time\' module was primarily used to time the server response time to ensure that we were within the defined specifications.
A logfile was created and timers created around each of the three components of the server response (start-up script, user input processing and forming the response HTML). It is important to note that the values were not written to the logfile until after the processing had finished (since the overhead I/O cost would skew the performance estimates).

The memory footprint of the CGI script was tested using the standard library module \emph{resource}. The module provides a memory-checking function called getrusage() that has an attribute ru_maxrss that gives total memory usage for the calling process. We were able to test that we met the specification set out for the CGI script (10 MB).

The aesthetic appeal and functionality were tested by demoing the website to sample users who provided feedback on the user experience and layout of the website. This was utilized to refine the design and add features (such as an explanation of how the emissions calculator works), in order to make the website more informative, easy-to-use and functional.

The website was also required to be able to handle errors gracefully. Every input box on the website was error-checked using JavaScript regular expressions to dynamically verify that the user had entered a valid input. If not, the user would be displayed a pop-up window that suggested they try another input. This was verified manually for the range of inputs that were deemed \"invalid\".

As for the backend, the testing was conducted on sub-networks of the larger SEPTA network to ensure that the nodes and trips were computed correctly. Once that was verified, the models were run on the full-scale system in order to ensure that the execution completed within a day (as determined by the frequency of baseball games). In addition, the models were run under memory-checking tools, including Valgrind (for the programming language C), in order to ensure that the model did not leak memory or utilize more than was specified in the system specification.

Demonstration
On demo day we had two deliverables: the project poster and the mock-up of the web application.
The poster aimed to provide a quick, concise overview of our project. It contained the abstract, a definition of the problem we are trying to solve and our project objectives. It also contained diagrams of the car network that we created, the backend and frontend system block diagrams as well as a sample block diagram for a specific subsystem (the SEPTA subsystem). We also discussed validation techniques that were utilized and presented some graphical results from our model to highlight the benefits of switching from cars to SEPTA.
The website was a basic web application that is described in detail in the Results section below. It is aimed at informing users about the tradeoff of choosing to take a car to the game in place of public transportation as well as providing information about the next home game and the weather at the time of the next home game. Additionally, alternative measures to reduce carbon impact are suggested for users who were averse to the switch. The website was created to be interactive, where judges and other observers were able to select from a limited set of zip codes to see how the user would interact with the finished product.
